Building socket-aware BPF programs

### 2018-10-27 paper/paper.tex
paper: Tidy up outro

The implementation intruduced in the 4.20 release cycle includes support for
looking up TCP and UDP sockets for IPv4 and IPv6 traffic, using the
\verb+SCHED_CLS+, \verb+SCHED_ACT+ and \verb+SK_SKB+ hook points. A proposed
patchset extends this to allow the same helpers to be used from the \verb+XDP+
hook points~\cite{sk-lookup-xdp}.

@@

This paper describes the contribution of two extensions to the Linux kernel BPF
implementation, firstly the introduction of reference tracking logic into the
verifier, which provides useful base infrastructure for supporting acquire and
release semantics for kernel resources, and secondly the socket lookup API
which may be now used from packet paths to allow BPF writers to build logic
based upon introspection of kernel sockets.

@@

The core BPF maintainers for their guidance and review of the patches.

>>>>

The implementation introduced in the 4.20 release cycle includes support for
looking up TCP and UDP sockets for IPv4 and IPv6 traffic, using the
\verb+SCHED_CLS+, \verb+SCHED_ACT+ and \verb+SK_SKB+ hook points. A proposed
patchset extends this to allow the same helpers to be used from the \verb+XDP+
hook points~\cite{sk-lookup-xdp}.

\todo{Associate custom metadata with socket?}

@@

This paper describes the contribution of new BPF verifier functionality in the
Linux kernel to track references to kernel resources and uses these to provide
access to socket introspection capabilities from packet handling hooks. The
introduction of reference tracking logic into the verifier provides
useful base infrastructure for supporting acquire and release semantics for
kernel resources which may prove useful for other helpers in future, and the
socket lookup API makes the packet hooks more powerful to support use cases
such as stateful firewalling or load-balancing based on the sockets that are
open on a system.

@@

The core BPF maintainers provided great guidance and review of the patches, in
particular Alexei Starovoitov, Daniel Borkmann and Martin KaFai Lau.
